Birth Spacing in the Presence of Son Preference and Sex-Selective \\ Abortions: India's Experience over Four Decades

### 2018-04-20 presentations/2018-paa-poster.tex
Combine results into one table

\usepackage{fontspec}
\setsansfont[Ligatures=TeX]{Gandhi Sans}
% \usepackage{unicode-math}
% \setmathfont{TeX Gyre Pagella Math}

@@

To complicate matters, shorter birth spacing after daughters may still 
be a representation of son preference for 
families who do not use prenatal sex selection.

@@

@@

\begin{block}{Spell Definition}

The first spell begins at the month of marriage, whereas the second and 
subsequent spells begin nine months after the previous birth.
All spells continue until either a child is born or censoring occurs.

I group spells into four periods based on the year of marriage
or year of the previous birth:
1972--1984, 1985--1994, 1995--2004, and 2005--2016.

@@

>>>>

\usepackage{fontspec}
\setsansfont[Ligatures=TeX]{Gandhi Sans}
% \usepackage{unicode-math}
% \setmathfont{TeX Gyre Pagella Math}
\usepackage{dcolumn}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{caption}

\newcommand{\mco}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\mct}[1]{\multicolumn{2}{c}{#1}}
\newcommand{\X}{$\times$ }
\newcommand{\hs}{\hspace{15pt}}

% Beamer thinks no table numbers and small text
\setbeamertemplate{caption}[numbered]
\captionsetup{font=large,labelfont=large}

@@

\vskip2ex
% 
% To complicate matters, shorter birth spacing after daughters may still 
% be a representation of son preference for 
% families who do not use prenatal sex selection.

@@

% \end{block}
% 
% \begin{block}{Spell Definition}

The first spell begins at the month of marriage, whereas the second and 
subsequent spells begin nine months after the previous birth.
All spells continue until either a child is born or censoring occurs.
I group spells into four periods based on the year of marriage
or year of the previous birth:
1972--1984, 1985--1994, 1995--2004, and 2005--2016.

@@

@@

\begin{table}[hp!]
\centering
\begin{threeparttable}
\caption{Estimated Median Duration and Sex Ratio}
\label{tab:median_sex_ratio_low}
\begin{tabular}{@{} c l D{.}{.}{2.3} D{.}{.}{2.3}  D{.}{.}{2.3} D{.}{.}{2.3} p{2ex} D{.}{.}{2.3} D{.}{.}{2.3}  D{.}{.}{2.3} D{.}{.}{2.3} @{}}
\toprule
                   &                            & \multicolumn{4}{c}{Rural Women -- No Education}                                                            & & \multicolumn{4}{c}{Urban Women -- 8+ Years of Education} \\  \cmidrule(lr){3-6} \cmidrule(lr){8-11}
                   &                            & \mct{1972--1984}                                    & \mct{2005--2016}                                     & & \mct{1972--1984}                                    & \mct{2005--2016}                                      \\ \cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){8-9} \cmidrule(lr){10-11} 
                   & \mco{Composition of}       & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}   & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}    & & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}   & \mco{Duration\tnote{a}}  & \mco{Percent\tnote{b}}     \\ 
 \mco{Spell}       & \mco{Prior Children}       & \mco{(Months)}  & \mco{Boys}                        & \mco{(Months)}  & \mco{Boys}                         & & \mco{(Months)}  & \mco{Boys}                        & \mco{(Months)}  & \mco{Boys}                          \\ \midrule
\multirow[c]{2}{*}{1} &                            &    26.2       &    52.1^{**}  &    24.4       &    51.5        &&    19.4       &    51.2       &    18.3       &    52.6^{***}  \\
                      &                            &    (0.2)      &    (0.3)      &    (0.1)      &    (0.4)       &&    (0.2)      &    (0.7)      &    (0.1)      &    (0.2)       \\
\addlinespace 
\multirow[c]{3}{*}{2} & \mco{One girl}             &    18.5       &    51.1       &    19.7       &    51.8        &&    19.2       &    52.1       &    27.1       &    56.1^{***}  \\
                      &                            &    (0.2)      &    (0.6)      &    (0.2)      &    (0.6)       &&    (0.2)      &    (1.4)      &    (0.3)      &    (0.9)       \\
                      & \mco{One boy}              &    19.6^{***} &    52.7^{**}  &    20.1^{*}   &    52.2^{*}    &&    20.1^{**}  &    52.0       &    26.6^{*}   &    49.9^{**}   \\
                      &                            &    (0.1)      &    (0.7)      &    (0.2)      &    (0.5)       &&    (0.5)      &    (1.0)      &    (0.3)      &    (0.6)       \\
\addlinespace 
\multirow[c]{5}{*}{3} & \mco{Two girls}            &    17.9       &    49.4^{*}   &    20.3       &    52.9^{**}   &&    20.7       &    54.5       &    29.1       &    65.6^{***}  \\
                      &                            &    (0.3)      &    (1.0)      &    (0.2)      &    (0.7)       &&    (0.7)      &    (4.2)      &    (0.7)      &    (1.3)       \\
                      & \mco{One boy / one girl}   &    19.1^{***} &    53.0^{**}  &    21.1^{***} &    51.8        &&    19.7       &    55.5^{**}  &    24.6^{***} &    55.8^{***}  \\
                      &                            &    (0.2)      &    (0.7)      &    (0.2)      &    (0.6)       &&    (0.4)      &    (1.7)      &    (0.9)      &    (0.6)       \\
                      & \mco{Two boys}             &    19.1^{***} &    51.4       &    22.0^{***} &    50.9        &&    20.3       &    49.3^{**}  &    25.5^{***} &    48.5        \\
                      &                            &    (0.2)      &    (0.9)      &    (0.3)      &    (0.8)       &&    (1.2)      &    (0.8)      &    (1.0)      &    (2.7)       \\
\addlinespace 
\bottomrule
\end{tabular}
\begin{tablenotes} 
\tiny
\item \hspace*{-0.5em} \textbf{Note.}
Bootstrapped standard errors shown in parentheses.
\item[a] For spells two and higher duration sex compositions other than all girls are 
tested against the duration for all girls, with *** indicating significantly different 
at the 1\% level, ** at the 5\% level, and * at the 10\% level, based on bootstrapped
differences.
\item[b] The predicted percent boys is tested against the natural percentage boys, 105 boys per 100 girls,
with *** indicating significantly different at the 1\% level, ** at the 5\% level, 
and * at 10\% level.
\end{tablenotes}
\end{threeparttable}
\end{table}
